Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-09 manuscript/manuscript.tex
sup reorg

\subsubsection{Block Bootstrap Procedure}
\label{supp:block-bootstrap}

@@

\subsubsection{Replicate $G$ and Partitioning the Variance in Allele Frequency}
\label{supp:replicate-g}

@@

\subsubsection{The Empirical Neutral Null Windowed Covariance Distribution}
\label{supp:empirical-null}

@@

\subsubsection{\textcite{Bergland2014-ij} Re-Analysis}
\label{supp:bergland-reanalysis}

@@

\subsubsection{Bias Correction for \textcite{Barghi2019-qy}}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/barghi-cov-panels.pdf}

@@

\subsection{\textcite{Barghi2019-qy} Trimmed Window Covariances}

Here we report median and trimmed mean of the windowed covariances. We note
that the median covariance is also limiting result of a trimmed mean that
symmetrically excludes the upper and lower $\alpha$ tails to calculate the
trimmed average windowed covariance. As $\alpha$ increases to 0.5, the trimmed
covariance converges to the median windowed covariance (by the definition of
the median; see Supplementary Figure \ref{suppfig:barghi-trimmed-mean}). Thus
our genomic temporal covariances are non-zero due to the impact of selection on
many genomic windows.

\begin{table}
  \centering
  \footnotesize
  \centering
  \begin{tabular}{l c c c c c c}

@@

@@

\subsubsection{\textcite{Barghi2019-qy} Empirical Null and Windowed Covariance Distributions}

@@

\clearpage
\subsubsection{\textcite{Barghi2019-qy} Tail Probabilities for Windowed Covariances Distributions}

>>>>

\subsection{Block Bootstrap Procedure}
\label{supp:block-bootstrap}

@@

\subsection{Replicate $G$ and Partitioning the Variance in Allele Frequency}
\label{supp:replicate-g}

@@

\subsection{The Empirical Neutral Null Windowed Covariance Distribution}
\label{supp:empirical-null}

@@

\subsection{\textcite{Bergland2014-ij} Re-Analysis}
\label{supp:bergland-reanalysis}

@@

\subsection{Bias Correction for \textcite{Barghi2019-qy}}

@@

\subsubsection{\textcite{Barghi2019-qy} Temporal Covariances Per Replicate}
\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/barghi-cov-panels.pdf}

@@

\subsection{\textcite{Barghi2019-qy} Trimmed Window Covariances}
\begin{table}
  \centering
  \footnotesize
  \centering
  \begin{tabular}{l c c c c c c}

@@

Here we report median and trimmed mean of the windowed covariances
(Supplementary Table \ref{supp:table-trimmed-mean}). We note that the median
covariance is also limiting result of a trimmed mean that symmetrically
excludes the upper and lower $\alpha$ tails to calculate the trimmed average
windowed covariance. As $\alpha$ increases to 0.5, the trimmed covariance
converges to the median windowed covariance (by the definition of the median;
see Supplementary Figure \ref{suppfig:barghi-trimmed-mean}). Thus our genomic
temporal covariances are non-zero due to the impact of selection on many
genomic windows.

@@

\subsection{\textcite{Barghi2019-qy} Empirical Null and Windowed Covariance Distributions}

@@

\clearpage
\subsection{\textcite{Barghi2019-qy} Tail Probabilities for Windowed Covariances Distributions}
